---
title: "Statistical Inference Project Part 2"
output: html_document
date: "Wednesday, April 22, 2015"
---


##Synopsis
This is the report of the second part of Peer assignment of Statistical inference of coursera.
The ToothGrowth dataset is the database collected based on the the Effect of Vitamin C on Tooth Growth in Guinea Pigs.
As described in R documentation, this ToothGrowth dataset recorded the response of the length of odontoblasts (teeth) in each of 10 guinea pigs at each of three dose levels of Vitamin C (0.5, 1, and 2 mg) with each of two delivery methods (orange juice or ascorbic acid).


##Result
###1. Load the ToothGrowth data and perform some basic exploratory data analyses.
**Answer :** 

```{r}
# load the neccessary libraries and dataset.
library(ggplot2)
library(datasets)
data(ToothGrowth)

# Take a glance at the loaded ToothGrowth dataset.
str(ToothGrowth)

# Verify the number of row as mentioned in R documentation.
nrow(ToothGrowth)

# Processing the variable dose of the dataset to factor.
ToothGrowth$dose <- as.factor(ToothGrowth$dose)

# re-look the processed dataset.
str(ToothGrowth)

```


###2. Show a basic summary of the data.
**Answer :** 

```{r}
# Show the summary statistics for the processed dataset.
summary(ToothGrowth)
```

There are 60 samples in this dataset and it consists of **len**, **supp** and **dose**.
The variable **len** is the length of odontoblasts (teeth) in each of 10 guinea pigs.
**supp** are the two delivery methods: orange juice (OJ) or ascorbic acid (VC).
**dose** is the three dose levels of Vitamin C (0.5, 1, and 2 mg) conducted for this test.

 

```{r}
# To use hypothesis tests to compare tooth growth by supp and dose, firstly split the cases into different dose levels and delivery methods.
table(ToothGrowth$dose, ToothGrowth$supp)
```


```{r}
# Display the tooth growth in delivery methods (supplement type).
ggplot(aes(x=dose, y=len), data=ToothGrowth) + geom_boxplot(aes(fill=dose))
ggplot(aes(x=supp, y=len), data=ToothGrowth) + geom_boxplot(aes(fill=supp))
```


```{r}
# Display the tooth growth in dose levels of Vitamin C.
#ggplot(aes(x=dose, y=len), data=ToothGrowth) + geom_boxplot(aes(fill=supp))

```


